---
title: "01-Data pre-processing and emission conversion"
author: "Joe Brown"
date: "2024-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal

The goal of this step in the workflow is to load and pre-process emissions data from the NDC experiment.

## Source utils 

```{r, sourcing all utils, message=F, warning=FALSE}
source("workflows/utils/source_all.R")

```

## Load in NDC experiment data 

```{r}
# GHG emissions
ndc_ghg_emissions <- load_ghg_data("workflows/data/raw-data/global_emissions.csv")

# LUC emissions 
ndc_luc_emissions <- load_luc_data("workflows/data/raw-data/global_LUC.csv")

```

### Process imported data

Split data by scenarios for the GHG and LUC emissions types and save data 

```{r, save emissions for each scenario}
# GHG emissions
ndc_ghg_list <- scenario_split(ndc_ghg_emissions, "workflows/data/input/scenarios_ghg")

# LUC emissions
ndc_luc_emissions <- scenario_split(ndc_luc_emissions, "workflows/data/input/scenarios_luc")

```

## Get emissions in Hector format

Hector formatted GHG emissions:

```{r, get ghg emissions in Hector format, message=FALSE}

# GHG emissions
hector_ghg_emissions <- lapply(ndc_ghg_list, function(scenario){
  
  # for each scenario in ghg_list get hector emissions
  h_ghg_emissions <- get_hector_emissions(scenario)
  
  # return the hector converted emissions
  return(h_ghg_emissions)
  
}) 

```

Hector formatted LUC emissions:

```{r, get luc emissions in Hector format, message=FALSE}
# LUC emissions
hector_luc_emissions <- lapply(ndc_luc_emissions, function(scenario){
  
  # for each scenario in luc_list get hector emissions
  h_luc_emissions <- get_luc_emissions(scenario)
  
  #return the hector converted emissions
  return(h_luc_emissions)
  
})
```

Bind together the GHG and LUC emissions after being converted to Hector format

```{r, bind together ghg and luc emissions data}
# bind ghg and luc emissions
all_emissions <- Map(rbind, hector_ghg_emissions, hector_luc_emissions)

```

## Build and save emissions constraints data 

Use `all_emissions` to format and save emissions constraint files. These file are not finalized because they will lack headers. 

```{r, build and save emissions constraint data, results='hide'}

lapply(all_emissions, function(scenario) {
  
  build_emissions_constraints_data(scenario)
  
})

```

