---
title: "02-Writing emissions constraints and input files"
author: "Joe Brown"
date: "2024-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal

The goal of this step in the workflow is to use the emissions constraint data located in `input/tables/raw-emissions_constraints` to write finalized emission constraint files (with headers) and then use them to write an input file for each scenario.

## Write emissions constraints files with headers

Create a list of files containing paths to raw emissions files: 

```{r, create a list of emissions constraint files}
emissions_directory <- "data/input/tables/raw-emissions_constraints/"

emissions_list <- list.files(emissions_directory, full.names = T)

```

Write emissions constraint files with headers for each file in emissions list:

```{r, write and save emissions constraints files with headers, results='hide'}
lapply(emissions_list, function(scenario) {
  
  # write emissions constraint file
  write_emissions_constraints_file(scenario)
  
})

```

New files are save in `input/tables/emissions_constraints`.

## Write emissions input files for Hector

Create a list of files containing paths to prepped emissions constraints files:

```{r, create a list of emissions constraints files, results='hide'}
constraints_directory <- "data/input/tables/emissions_constraints/"

emissions_constraints_list <- list.files(constraints_directory, full.names = T)

```

Write new input files using each emissions constraints file in the file list:
```{r, write new input files}
lapply(emissions_constraints_list, function(scenario) {
  
  # write input file 
  write_emissions_input_file(scenario)
  
})

```

