---
title: "03-Running Hector parameter uncertainty with NDC emissions input"
author: "Joe Brown"
date: "2024-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal

The goal of this document is to run Hector with Matilda using NDC emissions scenarios to compare with results from MAGICC7 used in Ou and Iyer 2021.

## Build list of input files

Build input file list of all the NDC experimental scenarios:

```{r, list files in ini directory}
input_file_directory <- "data/input/ini/"

input_files <- list.files(input_file_directory)

input_file_list <- list(T_01_BAU = paste0(input_file_directory, input_files[1]),
                    T_02_CAT_crnt = paste0(input_file_directory, input_files[2]), 
                    T_03_CAT_crnt = paste0(input_file_directory, input_files[3]),
                    T_04_NDC_cont = paste0(input_file_directory, input_files[4]), 
                    T_05_NDC_inc_LTS = paste0(input_file_directory, input_files[5]), 
                    T_06_NDC_cont = paste0(input_file_directory, input_files[6]),
                    T_07_NDC_inc_LTS = paste0(input_file_directory, input_files[7]))

```

## Matilda workflow

Use the NDC ini list to run Hector with the Matilda workflow.

### Build parameter set

```{r, construct perturbed parameter set}
# set seed for replication
set.seed(123)

# set sample size for param generation
n = 3000

# initiate a core that can be used to generate parameters -- here we will use SSP2-4.5
param_core <- newcore(system.file("input/hector_ssp245.ini", package = "hector"))

# generate param set
params <- generate_params(core = param_core,
                          draws = n)

write.csv(params, "data/output/initial_params.csv")
```

### Split jobs for parallel processing

```{r, split params into chunks and prepare cluster}
# splitting params df into chunks
param_chunks <- split(params, 1:1000)

# prep cluster
# initiate a cluster
cluster <- makeCluster(detectCores() - 1)

# export functions and objects to the core
clusterExport(cluster, c("input_file_list", 
                         "param_chunks", 
                         "newcore", 
                         "reset", 
                         "iterate_model"))

```

### Run the model
```{r, run the model with each ini file}

# run the model 
time_start = Sys.time()

model_result <- parLapply(cluster, names(input_file_list), function(scenario_name){

  # extract scenario information 
  scenario <- input_file_list[[scenario_name]]
  
  # initialize a model core for the current scenario
  core <- newcore(scenario, name = scenario_name)
  
  # run the model looking across param_chunks 
  result_list <- lapply(param_chunks, function(chunk) {
    
    iterate_model(core = core, 
                  params = chunk,
                  save_years = 1800:2100,
                  save_vars = c("gmst",
                                "CO2_concentration",
                                "global_tas",
                                "ocean_uptake"))
  })
  
  # reset core for each iteration
  reset(core)
  
  # Convert run_number to continuous among chunks 
  for (i in 2:length(result_list)) {
    
    # calculate the max run_number of the previous element in result_list
    max_run_number <- max(result_list[[i-1]]$run_number)
    
    # Add the max run_number of the previous element to the run_number of the current element
    result_list[[i]]$run_number <- result_list[[i]]$run_number + max_run_number
    
  }
  
  bind_result <- do.call(rbind, result_list)
  
  return(bind_result)
  
})

time_end = Sys.time() - time_start

```

Add names to the new list
```{r}
names(model_result) <- names(input_file_list)
```

Save the result:
```{r}
# save result as .RDS file
saveRDS(model_result, "data/output/model_result.RDS")

```

### Get normalized temperature (global_tas values)

Normalize temperature to pre-industrial reference period 1850-1900.

### Compute summary statistics

```{r}
## normalize the result 
model_result_normalized <- lapply(model_result, function(df) {
  
  norm_dat = normalize_to_reference(df, reference_start = 1850, reference_end = 1900)
  
  return(norm_dat)
  
  })

# get names 
names(model_result_normalized) <- names(model_result)

## subset to only include the variable of interest
gsat_data <- lapply(model_result_normalized, function(df) {
  
  subset_data = subset(df, variable == "global_tas")
  
  return(subset_data)
})

## compute summary statistics
summary_no_weighting <- lapply(names(gsat_data), function(scenario_names) {
  
  df = gsat_data[[scenario_names]]
  
  summary_no_wts <- df %>% 
  group_by(year) %>% 
  summarise(
    median = quantile(normalized_value, probs = 0.50), 
    ci_05 = quantile(normalized_value, probs = 0.05),
    ci_10 = quantile(normalized_value, probs = 0.10),
    ci_33 = quantile(normalized_value, probs = 0.33),
    ci_67 = quantile(normalized_value, probs = 0.67), 
    ci_90 = quantile(normalized_value, probs = 0.90), 
    ci_95 = quantile(normalized_value, probs = 0.95), 
    .groups = "drop"
  )
  
  summary_no_wts$scenario = scenario_names
  
  return(summary_no_wts)
  
})


```

### Plotting the results for Hector parameter uncertainty

```{r}
# bind data frames together 
no_weighting_plot_df <- do.call(rbind, summary_no_weighting)
no_weighting_plot_df <- subset(no_weighting_plot_df, year > 1994)

parametric_uncertainty_plot <- ggplot() +
  geom_ribbon(data = no_weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_10, 
                  ymax = ci_90), 
              fill = "grey", alpha = 0.5) +
  geom_ribbon(data = no_weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_33, 
                  ymax = ci_67), 
              fill = 'orange', alpha = 0.5) +
    geom_line(data = no_weighting_plot_df, 
            aes(x = year, y = median), 
            color = "black") +
  facet_wrap(~scenario)
parametric_uncertainty_plot

ggsave("no_weighting_exp_param_uncertainty.png",
       parametric_uncertainty_plot,
       device = "png", 
       dpi = 300)
```


```{r}
cmip6_dat <- read.csv("data/raw-data/cmip6_rslts.csv") %>% 
  select(-X)

cmip6_tas <- cmip6_dat %>% 
  filter(variable == "global_tas",
         scenario == "ssp245", 
         year > 1994)

cmip6_plot <- ggplot() +
  geom_line(data = cmip6_tas, aes(year, value, group = interaction(model), color = "CMIP6 ESM"), alpha = 0.5)
cmip6_plot
```


```{r}
no_weighting_plot_bau <- subset(no_weighting_plot_df, 
                               year > 1994 &
                                 scenario == "T_01_BAU")
magicc_bau <- read.csv("data/raw-data/T_01_BAU_magicc.csv")

parametric_uncertainty_bau <- ggplot() +
  # CMIP6 ESM lines
  geom_line(data = cmip6_tas, 
            aes(year, value, group = interaction(model), color = "CMIP6 ESM"), 
            alpha = 0.5, color = "darkgrey", linewidth = 0.3) +
  
  # No-weighting ribbons
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "grey", alpha = 0.4) +
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_33, ymax = ci_67), 
              fill = 'orange', alpha = 0.4) +
  
  # No-weighting median line
  geom_line(data = no_weighting_plot_bau, 
            aes(x = year, y = median, color = "Hector Median"), 
            color = "black") +
  
  # MAGICC lines and uncertainty
  geom_line(data = magicc_bau, 
            aes(x = year, y = value, color = "MAGICC Median"), 
            color = "red") +
  geom_ribbon(data = magicc_unc, 
              aes(x = year, ymin = lower, ymax = upper), 
              color = "red", linetype = "dashed", fill = NA, alpha = 0.2) +

  # Titles, labels, and theme
  labs(
    title = "Unconstrianed/Unweighted Parametric Uncertainty in BAU Scenario",
    x = "Year",
    y = "Temperature Anomaly (째C)",
    color = "Legend"
  ) +
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )

parametric_uncertainty_bau

ggsave("no_weighting_exp_param_uncertainty_BAU.png", 
       device = "png", 
       height = 7, 
       width = 10, 
       units = "in",
       dpi = 300)
```

Figure showing the entire ensemble (unweighted/unconstrianed):
```{r}
obs_temp <- data.frame(year = criterion_temp$years, value = criterion_temp$obs_values)

obs_temp_sd <- obs_temp %>% 
  mutate(sd = sd(value))

ggplot() +
  geom_line(data = subset(gsat_data$T_01_BAU, year > 1849), 
            aes(x = year, y = normalized_value, group = run_number, color = "Hector Ensemble (3000 member)"), alpha = 0.4,
          linewidth = 0.1) +
  geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
  geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
  
  # Adding the median and CI projection
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_05, ymax = ci_95), 
              fill = "red", alpha = 0.1) +
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "red", alpha = 0.2) +
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_33, ymax = ci_67), 
              fill = 'red', alpha = 0.4) +
  
  # No-weighting median line
  geom_line(data = no_weighting_plot_bau, 
            aes(x = year, y = median, color = "Hector Median")) +
  # Add labels and theme
  labs(
    title = "Unconstrained/Unweighted Hector Ensemble (BAU)",
    x = "Year",
    y = "Temperature Anomaly (째C)",
    color = "Legend"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Ensemble (3000 member)" = "grey",
      "Hector Median" = "darkred",
      "Historic Temperature (one SD)" = "navy"
    )
  ) +
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black")
  )

ggsave("unweighted_ensemble_bau.png", 
       device = "png", 
       height = 7, 
       width = 10, 
       units = "in",
       dpi = 300)
```
Figure showing the entire weighted/constrained ensemble:
```{r}
ggplot() +
  geom_line(
    data = subset(gsat_data$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Hector Ensemble (3000 member)"
    ),
    alpha = 0.4,
    linewidth = 0.1
  ) +
  geom_line(
    data = subset(gsat_data_normalized$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Constrained Ensemble (600 member)", 
      alpha = mc_weight
    ),
    linewidth = 0.1
  ) +
  scale_alpha_continuous(range(c(0.8, 1))) + # how extreme should the transparency gradient be - this is optional
  guides(alpha = "none") + # remove alpha legend 
  # Add labels and theme
  labs(
    title = "600-member Constrained Hector Ensemble (BAU)",
    x = "Year",
    y = "Temperature Anomaly (째C)",
    color = "Legend"
  ) +
  
  geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
  geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Ensemble (3000 member)" = "grey",
      "Constrained Ensemble (600 member)" = "#31A354",
      "Historic Temperature (one SD)" = "navy"
    )
  ) +
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black")
  )

 ggsave("constrained_ensemble_bau.png", 
        device = "png", 
        height = 7, 
        width = 10, 
        units = "in",
        dpi = 300)
```
Figure showing the entire weighted/constrained ensemble -- with median and range:
```{r}
ggplot() +
  geom_line(
    data = subset(gsat_data$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Hector Ensemble (3000 member)"
    ),
    alpha = 0.4,
    linewidth = 0.1
  ) +
  geom_line(
    data = subset(gsat_data_normalized$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Constrained Ensemble (600 member)", 
      alpha = mc_weight
    ),
    linewidth = 0.1
  ) +
  scale_alpha_continuous(range(c(0.8, 1))) + # how extreme should the transparency gradient be - this is optional
  guides(alpha = "none") + # remove alpha legend 
  # Add labels and theme
  labs(
    title = "600-member Constrained Hector Ensemble (BAU)",
    x = "Year",
    y = "Temperature Anomaly (째C)",
    color = "Legend"
  ) +
  
  geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
  geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
  
  # Adding the median and CI projection
  geom_ribbon(data = weighting_plot_bau, 
              aes(x = year, ymin = ci_05, ymax = ci_95), 
              fill = "red", alpha = 0.2) +
  geom_ribbon(data = weighting_plot_bau, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "red", alpha = 0.3) +
  geom_ribbon(data = weighting_plot_bau, 
              aes(x = year, ymin = ci_33, ymax = ci_67), 
              fill = 'red', alpha = 0.5) +
  
  # Median line
  geom_line(data = weighting_plot_bau, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # add magic range
  geom_ribbon(data = magicc_unc, 
              aes(x = year, ymin = lower, ymax = upper, color = "MAGICC Range"), fill = NA, linetype = "dashed", linewidth = 0.7) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Ensemble (3000 member)" = "grey",
      "Constrained Ensemble (600 member)" = "#31A354",
      "Historic Temperature (one SD)" = "navy", 
      "Hector Median" = "darkred", 
      "MAGICC Range" = "dodgerblue"
    )
  ) +
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black")
  )

ggsave("constrained_ensemble_bau_weighted_median_w_MAGICC.png",
       device = "png",
       height = 7,
       width = 10,
       units = "in",
       dpi = 300)
```

