---
title: "using_weighted_params"
author: "Joe Brown"
date: "2024-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal

The goal of this document is to run Hector with Matilda using NDC emissions scenarios. This analysis is meant to understand how the Hector + Matilda workflow can perform "ignorant" of MAGICC7 data. 

We will compare Hector + Matilda results against those from MAGICC7, published in in Ou and Iyer et al. 2021.

## Score model results

Compute scores for the normalized ensemble members against historical temperature & CO2 data. 

Load the `model_result` data if not already in global env.

Scoring:
```{r score model runs}

model_scores <- lapply(model_result, function(df) {
  
  temp_wt <- score_runs(df, criterion_temp, score_ramp, w1 = 0.01, w2 = 0.2)
  temp_wt <- na.omit(temp_wt)
  
  co2_wt <- score_runs(df, criterion_co2_obs(), score_ramp, w1 = 2, w2 = 10)
  co2_wt <- na.omit(co2_wt)
  
  score_list <- list(temp_wt, co2_wt)
  
  mc_score <- multi_criteria_weighting(score_list, criterion_weights = c(0.50, 0.50))
  
  return(mc_score)
})

```

Result is a list with each element corresponding to an emissions scenario. The data frames stored in each element contains scores for each ensemble member. Scores are computed using `score_ramp`. This function provides a score based on used defined "bounds" (w1 and w2). Ensemble members with an average abs difference < w1 are assigned a score of 1, indicating it is essentially equal to the observed data it is being scored against. Ensemble members with an average abs difference > w2 are assigned a score of 0, indicating the ensemble member is too different from the observed data to be considered reliable. All members between the w1-w2 bounds are scored whereby scores decrease linearly as the average abs difference increases.

Here the ensembles are scored against historical temperature, then historical CO2. A weighted "multi-criteria" score is computed to incorporate multiple lines of historical evidence into a single score.

## Filter to get top performing ensemble members

Filter the top 50% of ensembles by weight:
```{r}
top_scores <- lapply(model_scores, function(df){
  
  top_percentile <- quantile(df$mc_weight, 0.70)
  
  top_scores_magicc <- df %>%
  
    filter(mc_weight >= top_percentile)

})

```

This result will leave us with the top 2500 performing ensemble members based on their multi-criteria score.

Merge model weights with model results (for plotting later):
```{r}
weighted_ensemble <- Map(function(a, b) {
  
  merged <- merge(a, b, by = "run_number")
  
  return(merged)
  
}, model_result, top_scores)

```

## Computing summary stats
```{r, message=FALSE, warning=FALSE}
## subset to only include the variable of interest
gsat_data_weighted <- lapply(weighted_ensemble, function(df) {
  
  subset_data = subset(df, variable == "global_tas")
  
  return(subset_data)
})

## normalize gsat data 
gsat_data_normalized <- lapply(gsat_data_weighted, function(df) {
  
  normalize_to_reference(df, reference_start = 1850, reference_end = 1900)
  
}) 

## compute summary statistics
summary_weighting <- lapply(names(gsat_data_normalized), function(scenario_name) {
  
  df <- gsat_data_normalized[[scenario_name]]
  
  summary_wts <- df %>% 
  group_by(year) %>%
  summarise(
    median = quantile(normalized_value, probs = 0.50),
    ci_05 = quantile(normalized_value, probs = 0.05),
    ci_10 = quantile(normalized_value, probs = 0.10),
    ci_33 = quantile(normalized_value, probs = 0.33),
    ci_67 = quantile(normalized_value, probs = 0.67),
    ci_90 = quantile(normalized_value, probs = 0.90),
    ci_95 = quantile(normalized_value, probs = 0.95),
    .groups = "drop"
  ) %>% 
  subset(year > 1994)
  
  summary_wts$scenario <- scenario_name
  
  return(summary_wts)
  
})

```

This produces a list of summary statistic results. Each element of the list is a data frame of summary statistics for the median and different confidence bounds at each time step (1994-2100) for the `global_tas` variable, normalized to the 1850-1900 reference period.

## Plotting the results for scored and filtered Hector parameter uncertainty

```{r}
# bind data frames together 
weighting_plot_df <- do.call(rbind, summary_weighting)
weighting_plot_df <- subset(weighting_plot_df, year > 1994)

weighting_plot_df <- weighting_plot_df %>% 
  filter(!scenario %in% c("T_06_NDC_cont", "T_07_NDC_inc_LTS"))

parametric_uncertainty_plot_weighted <- ggplot() +
  # Ribbon for 10th-90th percentile
  geom_ribbon(data = weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_10, 
                  ymax = ci_90, fill = "Hector 10-90% CI"), 
              alpha = 0.5) +
  
  # Ribbon for 33rd-67th percentile
  geom_ribbon(data = weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_33, 
                  ymax = ci_67, fill = "Hector 33-67% CI"), 
              alpha = 0.5) +
  
  # Median line
  geom_line(data = weighting_plot_df, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = ou_data, 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # Facet by scenario
  facet_wrap(~scenario) +
  
  # Add labels and theme
  labs(
    title = "Constrained/Weighted Projections",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend", 
    fill = "Uncertainty Bound"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Median" = "black",
      "Ou and Iyer et al. 2021" = "red")) +
  
  scale_fill_manual(
    values = c(
      "Hector 33-67% CI" = "orange", 
      "Hector 10-90% CI" = "grey")) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 12), # Facet label size
    legend.position.inside = c(0.82, 0.2), # Manually position the legend
    legend.justification = "center"
  )

parametric_uncertainty_plot_weighted

ggsave("figures/filtered_hector_ensemble_summarized.png", 
       device = "png",
       height = 7, 
       width = 10, 
       units = "in",
       dpi = 300)
```

Using data from the BAU scenario to compare warming projections from unfiltered (unconstrianed), filtered (constrained), and MAGICC from Ou and Iyer et al. 2021:
```{r}
weighting_plot_bau <- subset(weighting_plot_df, 
                               year > 1994 &
                                 scenario == "T_01_BAU")

parametric_uncertainty_weighted_bau <- ggplot() +
  # CMIP6 ESM lines
  geom_line(data = cmip6_tas, 
            aes(year, value, group = interaction(model), color = "CMIP6 ESM"), 
            alpha = 0.2) +
  
  # Weighted uncertainty ribbons and median
  geom_ribbon(data = weighting_plot_bau, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "#3B9AB2", alpha = 0.1, color = "#3B9AB2", linetype = "dashed", linewidth = 0.5, show.legend = FALSE) +
  geom_line(data = weighting_plot_bau, 
            aes(x = year, y = median, color = "Weighted Median (Hector + Matilda)"), 
            linewidth = 0.7) +
  
  # MAGICC uncertainty ribbons and median
  geom_line(data = subset(ou_data, scenario == "T_01_BAU"), 
            aes(x = year, y = value, color = "MAGICC Median"), 
            linewidth = 0.7) +
  geom_ribbon(data = magicc_unc, 
              aes(x = year, ymin = lower, ymax = upper), 
              color = "#F21A00", fill = NA, linetype = "dashed", show.legend = FALSE) +
  
  # No weighting ribbons and median
  geom_ribbon(data = no_weighting_plot_bau, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "#EBCC2A", alpha = 0.1, color = "#EBCC2A", linetype = "dashed", show.legend = FALSE) +
  geom_line(data = no_weighting_plot_bau, 
            aes(x = year, y = median, color = "Unweighted Median (Hector + Matilda)"), 
            linewidth = 0.7) +
  
  # Titles, labels, and theme
  labs(
    title = "Constrained/Weighted vs. Unconstrained/Unweighted BAU Scenario",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend"
  ) +
  
  # Custom legend colors
  scale_color_manual(
    values = c(
      "CMIP6 ESM" = "darkgrey",
      "MAGICC Median" = "#F21A00",
      "Weighted Median (Hector + Matilda)" = "#3B9AB2",
      "Unweighted Median (Hector + Matilda)" = "#EBCC2A"
    )
  ) +
  
  theme_light() +
   theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black")
  )


parametric_uncertainty_weighted_bau

ggsave("figures/BAU_filtered_and_unfiltered_hector_comparison_with_magicc.png", 
       device = "png", 
       height = 7, 
       width = 10, 
       units = "in",
       dpi = 300)

```



# Computing probability
### Define metrics of interest

```{r define metric for end of century warming}
warming_metric <- new_metric(var = "global_tas", years = 2100, op = median)
  
```

### Compute warming results 

```{r compute warming metrics}
warming_results <- lapply(gsat_data_normalized, function(df) {
  
  metric_result <- metric_calc(df, warming_metric)
  
  return(metric_result)
})
```

Merge metric values with model scores:
```{r build weighted metric dfs}
weighted_gsat_data <- Map(function(a, b) {
  
  merged <- merge(a, b, by = "run_number")
  
  return(merged)
  
}, warming_results, top_200_scores)

```

save weighted metric data:
```{r save weighterd metric data}
# saveRDS(weighted_gmst_data)

```

### Computing probabilities 

```{r computing probabilities}
# define temperature ranges of interest -- align with ou and Iyer 
temp_ranges <- c(1, 1.5, 2, 3, 4, Inf)

temp_probability <- lapply(names(weighted_gsat_data), function(scenario) {
  
  df <- weighted_gsat_data[[scenario]]
  
  # run prob_calc
  prob_results <- prob_calc(df$metric_result, 
                            bins = temp_ranges, 
                            scores = df$mc_weight)
  
  prob_results$scenario <- scenario
  
  return(prob_results)
})

```

Bind probability list:
```{r}
prob_bind <- do.call(rbind, temp_probability)

prob_bind <- prob_bind %>% 
  filter(!scenario %in% c("T_06_NDC_cont", "T_07_NDC_inc_LTS"))
```


```{r}
temp_cols <- c("darkgrey","lightgrey","salmon", "#B2182B","#67001F")

# order levels
scen_order <- c("T_05_NDC_inc_LTS", "T_04_NDC_cont","T_03_CAT_crnt", "T_02_CAT_crnt", "T_01_BAU")
prob_bind$scenario <- factor(prob_bind$scenario, levels = scen_order)

probability_plot <- 
  ggplot(data = prob_bind, # identify the data location
         aes(
           fill = bins, # how fill should be applied
           x = scenario, # what data goes on the x-axis
           y = probability)) + # what data goes on the y-axis
  # below we will be flipping the coord of the figure so right now the axes seem 
  # backwards from what we want.
  geom_bar(position = position_fill(reverse = T), # what type of plot we want and reverse the 
                                                  # stack order so cooler temps are on left
           stat = "identity", # we want the width of the bar pieces to be constrained by a value in the data
           width = 0.6) + # how wide do you want the bar - personal preference
  scale_y_continuous(breaks = seq(0.0, 1.0, 0.1)) + # set the number and interval of probability breaks
  scale_fill_manual(
    values = temp_cols, # indicate the color palette to use
    labels = c(         # edit labels for the legend
      expression(paste("1.0 to 1.5", ~degree, "C")),
      expression(paste("1.5 to 2.0", ~degree, "C")),
      expression(paste("2.0 to 3.0", ~degree, "C")),
      expression(paste("3.0 to 4.0", ~degree, "C")),
      expression(paste(" > 4.0", ~degree, "C"))),
    name = "Warming") + # name of the legend
  labs(y = "Probability",
       x = "Scenario", 
       title = "Probability of Warming") +
  coord_flip() + # flip the coordinates of the figure to make horizontal representation
  theme_light() + # set theme - personal preference 
  theme(legend.position = "bottom") # change legend position - personal preference

probability_plot

ggsave("constrained_probability_plot.png", 
       device = "png",
       dpi = 300, 
       height = 4)
```

