---
title: "Emulating MAGICC"
author: "Joe Brown"
date: "2025-01-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("utils/source_all.R")
```

# Goal

Use MAGICC data to run an analysis where Hector + Matilda "emulates" MAGICC. 

To do this:

1. Create a "MAGICC" criterion using the MAGICC warming data from Ou and Iyer. 

2. Use the criterion to weight the Hector ensemble from Matilda.

3. Plot full weighted ensemble -- median and uncertainty range. 

4. Plot constrained ensemble -- selecting the top X number of Hector runs based on weight.

5. Compare parameters of Hector vs. MAGICC emulated Hector.

To start, load `model_result.RDS` from the `data/output` directory.

# New Scoring Criterion using MAGICC

Create new MAGICC criterion:
```{r}
# load magicc data
magicc_data <- read.csv("data/raw-data/ou_Iyer_global_mean_temperature.csv")
magicc_data_bau <- magicc_data %>%
  subset(scenario == "T_01_BAU") %>% 
  select(-scenario)
  
# create new criterion
criterion_magicc <- new_criterion("global_tas", years = magicc_data_bau$year, obs_values = magicc_data_bau$value)
```

Score model results using magicc data:
```{r}
bau_data <- model_result$T_01_BAU

model_scores_magicc <- score_runs(bau_data, criterion = criterion_magicc, score_function = score_bayesian)

```

Filter the top 600 weights:
```{r}
top_600_scores_magicc <- model_scores_magicc[order(model_scores_magicc$weights, decreasing = TRUE), ][1:600, ]

```

merge model weights with model results (for plotting later):
```{r}

weighted_ensemble_magicc <- merge(bau_data, top_600_scores_magicc, by = "run_number")

```

### Computing summary stats
```{r}
## subset to only include the variable of interest
gsat_data_weighted_magicc <- subset(weighted_ensemble_magicc, variable == "global_tas")

## normalize gsat data 
gsat_data_normalized_magicc <- normalize_to_reference(gsat_data_weighted_magicc, reference_start = 1850, reference_end = 1900)

## compute summary statistics
summary_weighting_magicc <-  gsat_data_normalized_magicc %>%
  group_by(year) %>%
  summarise(
    median = quantile(normalized_value, probs = 0.50),
    ci_05 = quantile(normalized_value, probs = 0.05),
    ci_10 = quantile(normalized_value, probs = 0.10),
    ci_33 = quantile(normalized_value, probs = 0.33),
    ci_67 = quantile(normalized_value, probs = 0.67),
    ci_90 = quantile(normalized_value, probs = 0.90),
    ci_95 = quantile(normalized_value, probs = 0.95),
    .groups = "drop"
  ) %>% 
  subset(year > 1994)

```

## plotting the weighted results 
```{r}
magicc_emulated_plot_weighted <- ggplot() +
  
  # # Ribbon for 10th-90th percentile
  # geom_ribbon(data = summary_weighting_magicc, 
  #             aes(x = year, 
  #                 ymin = ci_10, 
  #                 ymax = ci_90), 
  #             fill = "grey", alpha = 0.5) +
  # 
  # # Ribbon for 33rd-67th percentile
  # geom_ribbon(data = summary_weighting_magicc, 
  #             aes(x = year, 
  #                 ymin = ci_33, 
  #                 ymax = ci_67), 
  #             fill = 'orange', alpha = 0.5) +
  
  # Median line
  geom_line(data = summary_weighting_magicc, 
            aes(x = year, y = median, color = "Hector (MAGICC Emulated) Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = subset(ou_data, scenario == "T_01_BAU"), 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # geom_ribbon(data = magicc_unc, 
  #             aes(x = year, ymin = lower, ymax = upper), 
  #             color = "red", linetype = "dashed", fill = NA, alpha = 0.2) +
  
  # Add labels and theme
  labs(
    title = "Constrained/Weighted Projections -- MAGICC Emulation",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector (MAGICC Emulated) Median" = "black",
      "Ou and Iyer et al. 2021" = "red"
    )
  ) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 12), # Facet label size
    legend.position = c(0.2, 0.8), # Manually position the legend
    legend.justification = "center"
  )

magicc_emulated_plot_weighted

```


# Weighted parameters

Now merge the weights of this analysis with initial params. This will give the weights to the parameter sets that produce a median that is close to MAGICC. 

Compare the updated parameter range to the initial parameter range.

```{r}
params$run_number <- 1:nrow(params)

magicc_emulated_params <- merge(params, top_600_scores_magicc, by = "run_number")

param_summary_magicc_emulated <- data.frame(
  BETA = mean(magicc_emulated_params$BETA),
  BETA_sd = sd(magicc_emulated_params$BETA), 
  Q10_RH = mean(magicc_emulated_params$Q10_RH), 
  Q10_RH_sd = sd(magicc_emulated_params$Q10_RH), 
  NPP_FLUX0 = mean(magicc_emulated_params$NPP_FLUX0), 
  NPP_FLUX0_sd = sd(magicc_emulated_params$NPP_FLUX0), 
  AERO_SCALE = mean(magicc_emulated_params$AERO_SCALE), 
  AERO_SCALE_sd = sd(magicc_emulated_params$AERO_SCALE), 
  DIFFUSIVITY = mean(magicc_emulated_params$DIFFUSIVITY), 
  DIFFUSIVITY_sd = sd(magicc_emulated_params$DIFFUSIVITY), 
  ECS = mean(magicc_emulated_params$ECS), 
  ECS_sd = sd(magicc_emulated_params$ECS)
)

write.csv(param_summary_magicc_emulated, "data/output/magicc_emulated_param_summary.csv")
```

Should be able to use the new parameter set as the baseline for a new sampling.

### Build parameter set with MAGICC emulated parameter priors:

```{r, construct perturbed parameter set}
# set seed for replication
set.seed(123)

# set sample size for param generation
n = 3000

# generate param set
magicc_params <- sample_emulated_params(param_summary_magicc_emulated, draws = n)

write.csv(magicc_params, "data/output/magicc_params.csv")
```

### Split jobs for parallel processing

```{r, split params into chunks and prepare cluster}
# splitting params df into chunks
param_chunks <- split(magicc_params, 1:1000)

# prep cluster
# initiate a cluster
cluster <- makeCluster(detectCores() - 1)

# export functions and objects to the core
clusterExport(cluster, c("input_file_list", 
                         "param_chunks", 
                         "newcore", 
                         "reset", 
                         "iterate_model"))

```

### Run the model
```{r, run the model with each ini file}

# run the model 
time_start = Sys.time()

magicc_emulated_model_result <- parLapply(cluster, names(input_file_list), function(scenario_name){

  # extract scenario information 
  scenario <- input_file_list[[scenario_name]]
  
  # initialize a model core for the current scenario
  core <- newcore(scenario, name = scenario_name)
  
  # run the model looking across param_chunks 
  result_list <- lapply(param_chunks, function(chunk) {
    
    iterate_model(core = core, 
                  params = chunk,
                  save_years = 1800:2100,
                  save_vars = c("gmst",
                                "CO2_concentration",
                                "global_tas",
                                "ocean_uptake"))
  })
  
  # reset core for each iteration
  reset(core)
  
  # Convert run_number to continuous among chunks 
  for (i in 2:length(result_list)) {
    
    # calculate the max run_number of the previous element in result_list
    max_run_number <- max(result_list[[i-1]]$run_number)
    
    # Add the max run_number of the previous element to the run_number of the current element
    result_list[[i]]$run_number <- result_list[[i]]$run_number + max_run_number
    
  }
  
  bind_result <- do.call(rbind, result_list)
  
  return(bind_result)
  
})

time_end = Sys.time() - time_start

```

Add names to the new list
```{r}
names(magicc_emulated_model_result) <- names(input_file_list)
```

Save the result:
```{r}
# save result as .RDS file
saveRDS(magicc_emulated_model_result, "data/output/magicc_emulated_model_result.RDS")

```

### Get normalized temperature (global_tas values)

Normalize temperature to pre-industrial reference period 1850-1900.

### Compute summary statistics

```{r}
## normalize the result 
model_result_normalized <- lapply(model_result, function(df) {
  
  norm_dat = normalize_to_reference(df, reference_start = 1850, reference_end = 1900)
  
  return(norm_dat)
  
  })

# get names 
names(model_result_normalized) <- names(model_result)

## subset to only include the variable of interest
gsat_data <- lapply(model_result_normalized, function(df) {
  
  subset_data = subset(df, variable == "global_tas")
  
  return(subset_data)
})

## compute summary statistics
summary_no_weighting <- lapply(names(gsat_data), function(scenario_names) {
  
  df = gsat_data[[scenario_names]]
  
  summary_no_wts <- df %>% 
  group_by(year) %>% 
  summarise(
    median = quantile(normalized_value, probs = 0.50), 
    ci_05 = quantile(normalized_value, probs = 0.05),
    ci_10 = quantile(normalized_value, probs = 0.10),
    ci_33 = quantile(normalized_value, probs = 0.33),
    ci_67 = quantile(normalized_value, probs = 0.67), 
    ci_90 = quantile(normalized_value, probs = 0.90), 
    ci_95 = quantile(normalized_value, probs = 0.95), 
    .groups = "drop"
  )
  
  summary_no_wts$scenario = scenario_names
  
  return(summary_no_wts)
  
})


```
