---
title: "Emulating MAGICC"
author: "Joe Brown"
date: "2025-01-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("utils/source_all.R")
```

# Goal

Use MAGICC data to run an analysis where Hector + Matilda "emulates" MAGICC. 

To do this:

1. Create a "MAGICC" criterion using the MAGICC warming data from Ou and Iyer. 

2. Use the criterion to weight the Hector ensemble from Matilda.

3. Plot full weighted ensemble -- median and uncertainty range. 

4. Plot constrained ensemble -- selecting the top X number of Hector runs based on weight.

5. Compare parameters of Hector vs. MAGICC emulated Hector.

To start, load `model_result.RDS` from the `data/output` directory.

# New Scoring Criterion using MAGICC

Create new MAGICC criterion:
```{r}
# load magicc data
magicc_data <- read.csv("data/raw-data/ou_Iyer_global_mean_temperature.csv")

```

Create a list of magicc data that can be used to compute model scores for each scenario:
```{r}
magicc_data_list <- magicc_data %>%
  filter(!scenario %in% c("T_06_NDC_cont", "T_07_NDC_inc_LTS")) %>% 
  split(.$scenario) %>% 
  lapply(function(df) select(df, -scenario))

model_result[["T_06_NDC_cont"]] <- NULL
model_result[["T_07_NDC_inc_LTS"]] <- NULL
  
```

Create a criterion using each element in the magicc_data_list:
```{r}
# create new criterion
magicc_criterion_list <- lapply(magicc_data_list, function(df) {
    
  magicc_criterion <- new_criterion("global_tas", years = df$year, obs_values = df$value)
  
  return(magicc_criterion)

  })

```

Score model results using magicc data:
```{r}

model_scores_magicc <- Map(function(data, criterion, w1, w2) {
  
  score_list <- score_runs(data, criterion, score_ramp, w1, w2)

  return(score_list)
  
  }, model_result, magicc_criterion_list, MoreArgs = list(w1 = 0.2, w2 = 8.0))
  

```

## Filter to get top performing ensemble members

Filter the top 30% of ensembles by weight:
```{r}
top_magicc_scores <- lapply(model_scores_magicc, function(df){
  
  top_percentile <- quantile(df$weights, 0.15)
  
  top_magicc_scores <- df %>%
  
    filter(weights >= top_percentile)

})

```

This result leaves us with the top 1250 performing ensemble members based on their deviation from magicc projections.


Merge model weights with model results (for plotting later):
```{r}
weighted_ensemble_magicc <- Map(function(a, b) {
  
  merged <- merge(a, b, by = "run_number")
  
  return(merged)
  
}, model_result, top_magicc_scores)

```

## Computing summary stats
```{r, message=FALSE, warning=FALSE}
## subset to only include the variable of interest
gsat_data_weighted_magicc <- lapply(weighted_ensemble_magicc, function(df) {
  
  subset_data = subset(df, variable == "global_tas")
  
  return(subset_data)
})

## normalize gsat data 
gsat_data_normalized_magicc <- lapply(gsat_data_weighted_magicc, function(df) {
  
  normalize_to_reference(df, reference_start = 1850, reference_end = 1900)
  
}) 

## compute summary statistics
summary_weighting_magicc <- lapply(names(gsat_data_normalized_magicc), function(scenario_name) {
  
  df <- gsat_data_normalized_magicc[[scenario_name]]
  
  summary_wts <- df %>% 
  group_by(year) %>%
  summarise(
    median = quantile(normalized_value, probs = 0.50),
    ci_05 = quantile(normalized_value, probs = 0.05),
    ci_10 = quantile(normalized_value, probs = 0.10),
    ci_33 = quantile(normalized_value, probs = 0.33),
    ci_67 = quantile(normalized_value, probs = 0.67),
    ci_90 = quantile(normalized_value, probs = 0.90),
    ci_95 = quantile(normalized_value, probs = 0.95),
    .groups = "drop"
  ) %>% 
  subset(year > 1994)
  
  summary_wts$scenario <- scenario_name
  
  return(summary_wts)
  
})

```

```{r}
# bind data frames together 
weighting_magicc_plot_df <- do.call(rbind, summary_weighting_magicc)
weighting_magicc_plot_df <- subset(weighting_magicc_plot_df, year > 1994)

plot_magicc_weighted <- ggplot() +
  # Ribbon for 10th-90th percentile
  geom_ribbon(data = weighting_magicc_plot_df, 
              aes(x = year, 
                  ymin = ci_10, 
                  ymax = ci_90, fill = "Hector 10-90% CI"), 
              alpha = 0.5) +
  
  # Ribbon for 33rd-67th percentile
  geom_ribbon(data = weighting_magicc_plot_df, 
              aes(x = year, 
                  ymin = ci_33, 
                  ymax = ci_67, fill = "Hector 33-67% CI"), 
              alpha = 0.5) +
  
  # Median line
  geom_line(data = weighting_magicc_plot_df, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = ou_data, 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # Facet by scenario
  facet_wrap(~scenario) +
  
  # Add labels and theme
  labs(
    title = "Constrained/Weighted Projections",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend", 
    fill = "Uncertainty Bound"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Median" = "black",
      "Ou and Iyer et al. 2021" = "red")) +
  
  scale_fill_manual(
    values = c(
      "Hector 33-67% CI" = "orange", 
      "Hector 10-90% CI" = "grey")) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 12), # Facet label size
    legend.position.inside = c(0.82, 0.2), # Manually position the legend
    legend.justification = "center"
  )

plot_magicc_weighted

# ggsave("figures/magicc_emulation_wide_ecs_exp_BAU.png",
#        magicc_emulated_plot_weighted,
#        device = "png",
#        height = 7,
#        width = 10,
#        units = "in",
#        dpi = 300)
```

## Magic emulated figure

Figure showing the entire weighted/constrained ensemble:
```{r}
# magicc_emulated_weighted_ensemble_bau <- 
#   ggplot() +
#   geom_line(
#     data = subset(gsat_data$T_01_BAU, year > 1849),
#     aes(
#       x = year,
#       y = normalized_value,
#       group = run_number,
#       color = "Hector Ensemble (5000 member)"
#     ),
#     alpha = 0.4,
#     linewidth = 0.1
#   ) +
#   geom_line(
#     data = subset(gsat_data_normalized_magicc, year > 1849),
#     aes(
#       x = year,
#       y = normalized_value,
#       group = run_number,
#       color = "Constrained Ensemble (4500 member)", 
#       alpha = weights
#     ),
#     linewidth = 0.1
#   ) +
#   scale_alpha_continuous(range(c(0.8, 1))) + # how extreme should the transparency gradient be - this is optional
#   guides(alpha = "none") + # remove alpha legend 
#   # Add labels and theme
#   labs(
#     title = "4500-member Constrained Hector Ensemble (BAU)",
#     x = "Year",
#     y = "Temperature Anomaly (°C)",
#     color = "Legend"
#   ) +
#   
#   geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
#   geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
#   
#   # Add custom colors for the legend
#   scale_color_manual(
#     values = c(
#       "Hector Ensemble (5000 member)" = "grey",
#       "Constrained Ensemble (4500 member)" = "#31A354",
#       "Historic Temperature (one SD)" = "navy"
#     )
#   ) +
#   theme_light() +
#   theme(
#     plot.title = element_text(size = 16, face = "bold"),
#     axis.title = element_text(size = 14),
#     axis.text = element_text(size = 12),
#     legend.title = element_text(size = 10),
#     legend.text = element_text(size = 8),
#     legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
#     legend.justification = c(0, 1), # Align legend's top-left corner
#     legend.background = element_rect(fill = "white", color = "black")
#   )
# 
# magicc_emulated_weighted_ensemble_bau
# 
#  ggsave("figures/constrained_magicc_emulated_ensemble_bau.png",
#         magicc_emulated_weighted_ensemble_bau,
#         device = "png",
#         height = 7,
#         width = 10,
#         units = "in",
#         dpi = 300)
```

Figure showing the entire weighted/constrained ensemble -- with median and range:
```{r}
ensemble_plot_data_magicc <- lapply(gsat_data_normalized_magicc, function(df) {
  
  data_subset <- subset(df, year > 1849)
  
  return(data_subset)

})

ensemble_plot_magicc_df <- do.call(rbind, ensemble_plot_data_magicc)

full_magicc_emulated_ensemble_constrained <- 
  ggplot() +
  geom_line(
    data = ensemble_plot_magicc_df,
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Hector Ensemble (5000 member)"
    ),
    alpha = 0.4,
    linewidth = 0.1
  ) +
  geom_line(
    data = ensemble_plot_magicc_df,
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Constrained Ensemble (4500 member)", 
      alpha = weights
    ),
    linewidth = 0.1
  ) +
  scale_alpha_continuous(range(c(0.8, 1))) + # how extreme should the transparency gradient be - this is optional
  guides(alpha = "none") + # remove alpha legend 
  # Add labels and theme
  labs(
    title = "4500-member Constrained Hector Ensemble (BAU)",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend"
  ) +
  
  geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
  geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
  
  # Adding the median and CI projection
  geom_ribbon(data = weighting_magicc_plot_df, 
              aes(x = year, ymin = ci_05, ymax = ci_95), 
              fill = "red", alpha = 0.2) +
  geom_ribbon(data = weighting_magicc_plot_df, 
              aes(x = year, ymin = ci_10, ymax = ci_90), 
              fill = "red", alpha = 0.3) +
  geom_ribbon(data = weighting_magicc_plot_df, 
              aes(x = year, ymin = ci_33, ymax = ci_67), 
              fill = 'red', alpha = 0.5) +
  
  # Median line
  geom_line(data = weighting_magicc_plot_df, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = ou_data, 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Ensemble (5000 member)" = "grey",
      "Constrained Ensemble (4500 member)" = "#31A354",
      "Historic Temperature (one SD)" = "navy", 
      "Hector Median" = "darkred",
      "Ou and Iyer et al. 2021" = "dodgerblue"
    )
  ) +
  facet_wrap(~scenario) +
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.99, 0.01),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black")
  )

full_magicc_emulated_ensemble_constrained

# ggsave("figures/full_magicc_emulated_ensemble_constrained.png",
#        full_magicc_emulated_ensemble_constrained,
#        device = "png",
#        height = 7,
#        width = 10,
#        units = "in",
#        dpi = 300)
```
```{r}
scored_bau_ensemble_magicc <- 
  ggplot() +
  geom_line(
    data = subset(gsat_data$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Hector Ensemble (5000 member)"
    ),
    alpha = 0.4,
    linewidth = 0.1
  ) +
  geom_line(
    data = subset(gsat_data_normalized_magicc$T_01_BAU, year > 1849),
    aes(
      x = year,
      y = normalized_value,
      group = run_number,
      color = "Constrained Ensemble (1500 member)" 
    ), linewidth = 0.1, alpha = 0.3) + 
  
  # Adding Historic temperature observations
  geom_line(data = obs_temp, aes(x = year, y = value, color = "Historic Temperature (one SD)")) +
  geom_ribbon(data = obs_temp_sd, aes(x = year, ymin = value - sd, ymax = value + sd), alpha = 0.3, fill = "navy") +
  
  # Adding the median and CI projection
  geom_ribbon(data = subset(weighting_magicc_plot_df, scenario == "T_01_BAU"), 
              aes(x = year, ymin = ci_33, ymax = ci_67, alpha = "Hector 33-67%"), 
              fill = 'red') +
  geom_ribbon(data = subset(weighting_magicc_plot_df, scenario == "T_01_BAU"), 
              aes(x = year, ymin = ci_10, ymax = ci_90, alpha = "Hector 10-90%"), 
              fill = "red") +
  geom_ribbon(data = subset(weighting_magicc_plot_df, scenario == "T_01_BAU"), 
              aes(x = year, ymin = ci_05, ymax = ci_95, alpha = "Hector 05-95%"), 
              fill = "red") +
  
  # Median line
  geom_line(data = subset(weighting_magicc_plot_df, scenario == "T_01_BAU"), 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # add magic range
  geom_ribbon(data = magicc_unc, 
              aes(x = year, ymin = lower, ymax = upper, color = "MAGICC Range"), fill = NA, linetype = "dashed", linewidth = 0.7) +
  
    # Ou and Iyer et al. 2021 line
  geom_line(data = subset(ou_data, scenario == "T_01_BAU"), 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
      # Add labels and theme
  labs(
    title = "1500-member MAGICC Emulation Hector Ensemble (BAU) ",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend", 
    alpha = "Uncertainty Bounds"
  ) +
  
  # Add custom colors and alpha level for the legend
  scale_color_manual(
    values = c(
      "Hector Ensemble (5000 member)" = "grey",
      "Constrained Ensemble (1500 member)" = "#31A354",
      "Historic Temperature (one SD)" = "navy", 
      "Hector Median" = "darkred", 
      "MAGICC Range" = "dodgerblue", 
    "Ou and Iyer et al. 2021" = "dodgerblue")) +
  scale_alpha_manual(
    values = c(
      "Hector 33-67%" = 0.4, 
      "Hector 10-90%" = 0.3, 
      "Hector 05-95%" = 0.2)) +
  
    # Explicitly set legend order
  guides(
    color = guide_legend(order = 1),  # First in legend
    alpha = guide_legend(order = 2)   # Second in legend
  ) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = c(0.01, 0.99),  # Use this to place the legend inside the panel
    legend.justification = c(0, 1), # Align legend's top-left corner
    legend.background = element_rect(fill = "white", color = "black"), 
    legend.spacing.y = unit(0.1, "cm")
  )

scored_bau_ensemble_magicc
```

## Define metrics of interest

We define a warming metric to give us median warming in the year 2100 give the filtered Hector ensemble.

```{r define metric for end of century warming}
warming_metric <- new_metric(var = "global_tas", years = 2100, op = median)
  
```

## Compute warming results 

Using the `metric_calc` function we compute the warming results.
```{r compute warming metrics}
warming_results_magicc <- lapply(gsat_data_normalized_magicc, function(df) {
  
  metric_result <- metric_calc(df, warming_metric)
  
  return(metric_result)
})
```

Now we merge the median warming values with scores which will allow us to compute probabilities while also considering how well each ensemble member performs against historical observations:
```{r build weighted metric dfs}
weighted_gsat_data_magicc <- Map(function(a, b) {
  
  merged <- merge(a, b, by = "run_number", all.x = TRUE)
  
  return(merged)
  
}, warming_results_magicc, top_magicc_scores)

```

We can save these results if desired:
```{r save weighterd metric data}

```

## Computing probabilities 

```{r computing probabilities}
# define temperature ranges of interest -- align with Ou and Iyer et al. 2021
temp_ranges <- c(1, 1.5, 2, 3, 4, Inf)

temp_probability_magicc <- lapply(names(weighted_gsat_data_magicc), function(scenario) {
  
  df <- weighted_gsat_data_magicc[[scenario]]
  
  # run prob_calc
  prob_results <- prob_calc(df$metric_result, 
                            bins = temp_ranges, 
                            scores = df$weights)
  
  prob_results$scenario <- scenario
  
  return(prob_results)
})

```

Bind probability list:
```{r}
prob_bind_magicc <- do.call(rbind, temp_probability_magicc)

prob_bind_magicc <- prob_bind_magicc %>% 
  filter(!scenario %in% c("T_06_NDC_cont", "T_07_NDC_inc_LTS"))
```


```{r}
temp_cols <- c("darkgrey","lightgrey","salmon", "#B2182B","#67001F")

# order levels
scen_order <- c("T_05_NDC_inc_LTS", "T_04_NDC_cont","T_03_CAT_crnt", "T_02_CAT_crnt", "T_01_BAU")
prob_bind_magicc$scenario <- factor(prob_bind_magicc$scenario, levels = scen_order)

probability_plot_magicc <- 
  ggplot(data = prob_bind_magicc, # identify the data location
         aes(
           fill = bins, # how fill should be applied
           x = scenario, # what data goes on the x-axis
           y = probability)) + # what data goes on the y-axis
  # below we will be flipping the coord of the figure so right now the axes seem 
  # backwards from what we want.
  geom_bar(position = position_fill(reverse = T), # what type of plot we want and reverse the 
                                                  # stack order so cooler temps are on left
           stat = "identity", # we want the width of the bar pieces to be constrained by a value in the data
           width = 0.6) + # how wide do you want the bar - personal preference
  scale_y_continuous(breaks = seq(0.0, 1.0, 0.1)) + # set the number and interval of probability breaks
  scale_fill_manual(
    values = temp_cols, # indicate the color palette to use
    labels = c(         # edit labels for the legend
      expression(paste("1.0 to 1.5", ~degree, "C")),
      expression(paste("1.5 to 2.0", ~degree, "C")),
      expression(paste("2.0 to 3.0", ~degree, "C")),
      expression(paste("3.0 to 4.0", ~degree, "C")),
      expression(paste(" > 4.0", ~degree, "C"))),
    name = "Warming") + # name of the legend
  labs(y = "Probability",
       x = "Scenario", 
       title = "Probability of Warming for MAGICC Emulation") +
  coord_flip() + # flip the coordinates of the figure to make horizontal representation
  theme_light() + # set theme - personal preference 
  theme(legend.position = "bottom") # change legend position - personal preference

probability_plot_magicc

```







## computing probabilisties

```{r}
# define metric
warming_metric <- new_metric(var = "global_tas", years = 2100, op = median)

# computing metrics 
metric_result_emulated <- metric_calc(gsat_data_normalized_magicc, warming_metric)

# merge metrics with top_scores
top_magicc_emulated_metrics <- merge(metric_result_emulated, top_scores_magicc, by = "run_number")

# define temperature ranges of interest -- align with ou and Iyer 
temp_ranges <- c(1, 1.5, 2, 3, 4, Inf)

# run prob_calc
prob_results <- prob_calc(top_magicc_emulated_metrics$metric_result,
                          bins = temp_ranges,
                          scores = top_magicc_emulated_metrics$weights)
```


Plotting probability
```{r}
temp_cols <- c("lightgrey","salmon", "#B2182B","#67001F")

# order levels
prob_results$scenario <- "T_01_BAU"

probability_plot <- 
  ggplot(data = prob_results, # identify the data location
         aes(
           fill = bins, # how fill should be applied
           x = scenario, # what data goes on the x-axis
           y = probability)) + # what data goes on the y-axis
  # below we will be flipping the coord of the figure so right now the axes seem 
  # backwards from what we want.
  geom_bar(position = position_fill(reverse = T), # what type of plot we want and reverse the 
                                                  # stack order so cooler temps are on left
           stat = "identity", # we want the width of the bar pieces to be constrained by a value in the data
           width = 0.6) + # how wide do you want the bar - personal preference
  scale_y_continuous(breaks = seq(0.0, 1.0, 0.1)) + # set the number and interval of probability breaks
  scale_fill_manual(
    values = temp_cols, # indicate the color palette to use
    labels = c(         # edit labels for the legend
      expression(paste("1.5 to 2.0", ~degree, "C")),
      expression(paste("2.0 to 3.0", ~degree, "C")),
      expression(paste("3.0 to 4.0", ~degree, "C")),
      expression(paste(" > 4.0", ~degree, "C"))),
    name = "Warming") + # name of the legend
  labs(y = "Probability",
       x = "Scenario", 
       title = "Probability of Warming") +
  coord_flip() + # flip the coordinates of the figure to make horizontal representation
  theme_light() + # set theme - personal preference 
  theme(legend.position = "bottom") # change legend position - personal preference

probability_plot

ggsave("figures/constrained_probability_plot.png", 
       probability_plot,
       device = "png",
       dpi = 300, 
       height = 4)
```




## NEED TO RUN THE ABOVE ANALYSIS ACROSS ALL SCENARIOS BEFORE RUNNING THIS PLOT
```{r}
weighting_plot_df_emulated <- summary_weighting_magicc %>% 
  filter(!scenario %in% c("T_06_NDC_cont", "T_07_NDC_inc_LTS"))

# load ou and Iyer data
ou_data <- read.csv("data/raw-data/ou_Iyer_global_mean_temperature.csv")

parametric_uncertainty_plot_weighted <- ggplot() +
  # Ribbon for 10th-90th percentile
  geom_ribbon(data = weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_10, 
                  ymax = ci_90), 
              fill = "grey", alpha = 0.5) +
  
  # Ribbon for 33rd-67th percentile
  geom_ribbon(data = weighting_plot_df, 
              aes(x = year, 
                  ymin = ci_33, 
                  ymax = ci_67), 
              fill = 'orange', alpha = 0.5) +
  
  # Median line
  geom_line(data = weighting_plot_df, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = ou_data, 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # Facet by scenario
  facet_wrap(~scenario) +
  
  # Add labels and theme
  labs(
    title = "Constrained/Weighted Projections",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector Median" = "black",
      "Ou and Iyer et al. 2021" = "red"
    )
  ) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 12), # Facet label size
    legend.position.inside = c(0.82, 0.2), # Manually position the legend
    legend.justification = "center"
  )

parametric_uncertainty_plot_weighted


ggsave("emissions_projections_weighted.png", 
       device = "png",
       height = 7, 
       width = 10, 
       units = "in",
       dpi = 300)
```

