---
title: "Emulating MAGICC"
author: "Joe Brown"
date: "2025-01-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("utils/source_all.R")
```

# Goal

Use MAGICC data to run an analysis where Hector + Matilda "emulates" MAGICC. 

To do this:

1. Create a "MAGICC" criterion using the MAGICC warming data from Ou and Iyer. 

2. Use the criterion to weight the Hector ensemble from Matilda.

3. Plot full weighted ensemble -- median and uncertainty range. 

4. Plot constrained ensemble -- selecting the top X number of Hector runs based on weight.

5. Compare parameters of Hector vs. MAGICC emulated Hector.

To start, load `model_result.RDS` from the `data/output` directory.

# New Scoring Criterion using MAGICC

Create new MAGICC criterion:
```{r}
# load magicc data
magicc_data <- read.csv("data/raw-data/ou_Iyer_global_mean_temperature.csv")
magicc_data_bau <- magicc_data %>%
  subset(scenario == "T_01_BAU") %>% 
  select(-scenario)
  
# create new criterion
criterion_magicc <- new_criterion("global_tas", years = magicc_data_bau$year, obs_values = magicc_data_bau$value)
```

Score model results using magicc data:
```{r}
bau_data <- model_result$T_01_BAU

model_scores_magicc <- score_runs(bau_data, criterion = criterion_magicc, score_function = score_bayesian)

```

Filter the top 600 weights:
```{r}
top_600_scores_magicc <- model_scores_magicc[order(model_scores_magicc$weights, decreasing = TRUE), ][1:600, ]

```

merge model weights with model results (for plotting later):
```{r}

weighted_ensemble_magicc <- merge(bau_data, top_600_scores_magicc, by = "run_number")

```

### Computing summary stats
```{r}
## subset to only include the variable of interest
gsat_data_weighted_magicc <- subset(weighted_ensemble_magicc, variable == "global_tas")

## normalize gsat data 
gsat_data_normalized_magicc <- normalize_to_reference(gsat_data_weighted_magicc, reference_start = 1850, reference_end = 1900)

## compute summary statistics
summary_weighting_magicc <-  gsat_data_normalized_magicc %>%
  group_by(year) %>%
  summarise(
    median = weighted.quantile(normalized_value, w = weights, probs = 0.50),
    ci_05 = weighted.quantile(normalized_value, w = weights, probs = 0.05),
    ci_10 = weighted.quantile(normalized_value, w = weights, probs = 0.10),
    ci_33 = weighted.quantile(normalized_value, w = weights, probs = 0.33),
    ci_67 = weighted.quantile(normalized_value, w = weights, probs = 0.67),
    ci_90 = weighted.quantile(normalized_value, w = weights, probs = 0.90),
    ci_95 = weighted.quantile(normalized_value, w = weights, probs = 0.95),
    .groups = "drop"
  )

```

## plotting the weighted results 
```{r}
magicc_emulated_plot_weighted <- ggplot() +
  # Ribbon for 10th-90th percentile
  geom_ribbon(data = summary_weighting_magicc, 
              aes(x = year, 
                  ymin = ci_10, 
                  ymax = ci_90), 
              fill = "grey", alpha = 0.5) +
  
  # Ribbon for 33rd-67th percentile
  geom_ribbon(data = summary_weighting_magicc, 
              aes(x = year, 
                  ymin = ci_33, 
                  ymax = ci_67), 
              fill = 'orange', alpha = 0.5) +
  
  # Median line
  geom_line(data = summary_weighting_magicc, 
            aes(x = year, y = median, color = "Hector Median"), 
            linewidth = 0.7) +
  
  # Ou and Iyer et al. 2021 line
  geom_line(data = ou_data, 
            aes(x = year, y = value, color = "Ou and Iyer et al. 2021"), 
            linewidth = 0.7) +
  
  # Add labels and theme
  labs(
    title = "Constrained/Weighted Projections -- MAGICC Emulation",
    x = "Year",
    y = "Temperature Anomaly (°C)",
    color = "Legend"
  ) +
  
  # Add custom colors for the legend
  scale_color_manual(
    values = c(
      "Hector (MAGICC Emulated) Median" = "black",
      "Ou and Iyer et al. 2021" = "red"
    )
  ) +
  
  theme_light() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 12), # Facet label size
    legend.position = c(0.82, 0.2), # Manually position the legend
    legend.justification = "center"
  )

magicc_emulated_plot_weighted